Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-09-19 article-models-ttderived.tex
added forgotten files

\subsubsection{Interactions of the composition threesome}
Our current goal is to show that the three sorts of composition are all
compatbile with each other. This includes showing associativity and interchange
properties. The following lemma of the composition threesome stands at the
basis of the further compatibility results.

@@

\begin{lem}
Consider a morphism $\jhom{{\Gamma}{A}}{{P}{Q}}{R}{f}$ and a morphism
$\jhom{\Gamma}{{A}{R}}{B}{g}$. Then the diagram
\begin{equation*}
\begin{tikzcd}
\ctxext{A}{{P}{Q}}
  \ar{r}{\jvcomp{}{\idtm{A}}{f}}
  \ar{dr}[swap]{\jcomp{}{f}{g}}
  &
\ctxext{A}{R}
  \ar{d}{g}
  \\
  &
B
\end{tikzcd}
\end{equation*}
in context $\Gamma$ commutes judgmentally.
\end{lem}

>>>>

\subsubsection{Interactions of horizontal and vertical composition}
Our current goal is to show that the three sorts of composition are all
compatbile with each other. This includes showing associativity and interchange
properties. The following lemma of the composition threesome stands at the
basis of the further compatibility results.

@@

\begin{lem}\label{lem:edom-edom-comp}
Consider a morphism $\jhom{{\Gamma}{A}}{{P}{Q}}{R}{f}$ and a morphism
$\jhom{\Gamma}{{A}{R}}{B}{g}$. Then the diagram
\begin{equation*}
\begin{tikzcd}
\ctxext{A}{{P}{Q}}
  \ar{r}{\jvcomp{}{\idtm{A}}{f}}
  \ar{dr}[swap]{\jcomp{}{f}{g}}
  &
\ctxext{A}{R}
  \ar{d}{g}
  \\
  &
B
\end{tikzcd}
\end{equation*}
in context $\Gamma$ commutes judgmentally.
\end{lem}
